Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-29 paper.tex
primeira nova versao final do artigo

If $\mathcal{N}_f$ is directed and has no self-loops, the probability
of an edge between two arbitrary vertices is $p_e=\frac{z}{N(N-1)}$ (see Appendix~\ref{ap:ded}). (a numeração de figuras, tabelas, apêndices, etc. tem que começar de 1 ou A)
A vertex in the ideal Erd\"os-R\'enyi digraph with the same number of vertices and edges, and thus the same probability $p_e$ for the presence of an edge, will have degree $k$ with probability:

@@

For the histograms used in the classification process, the use of at least $\eta$ vertices for each bin did not yield significant differences.
That was understood as a consequence of the observation scale (see Appendix~\ref{ap:ded2}).

@@

\section{Conclusions and further work}\label{sec:conc}
The characterization of interaction networks resulted from stability observations. Along temporal activity statistics, this work reports the stability of the formation of principal components and of the relative sizes of periphery, intermediary and hubs Erd\"os sectors. These results suggested typologies for both agents and the networks.

>>>>

If $\mathcal{N}_f$ is directed and has no self-loops, the probability
of an edge between two arbitrary vertices is $p_e=\frac{z}{N(N-1)}$.
A vertex in the ideal Erd\"os-R\'enyi digraph with the same number of vertices and edges, and thus the same probability $p_e$ for the presence of an edge, will have degree $k$ with probability:

@@

@@

\section{Conclusions and further work}\label{sec:conc}
The characterization of interaction networks resulted from stability observations. 
Along temporal activity statistics, this work reports the stability of the formation of principal components and of the relative sizes of periphery, intermediary and hubs Erd\"os sectors.
These results suggests and eases the observance of types in both agents and the networks.
